---
title: "ASN5.1. Modeling with Your Data"
author: "2023 FIRE298 Sustainability Analytics"
format: html
editor: visual
---

In this assignment, you will apply what you have learned about modeling with regressions in the spring semester and the DataCamp course "Modeling with the Tidyverse" to the dataset that your team has created. To learn more about the dataset, you will use regression analysis to **predict** the outcome variable.

### **Part 1. Explaining the Data**

Instructions: Run the script below to download and declare the required packages.

```{r}
#| message: false
install.packages("moderndive")
install.packages("tidyverse")
library("moderndive")
library("tidyverse")
```

Instructions: Upload your team's final dataframe into Posit Cloud. Use the read.csv function to upload the dataframe into the Posit Cloud Environment.

```{r}
df <- read.csv("finalnasa.csv")
```

**Question 1: What is the unit of each observation in the data? (2 points)**

Instructions: Identify which columns in the dataset make each observation unique. Usually, there is a column indicating geographical locations and another column showing the frequency of the data. For an example, you can look at asn-6-4-key.qmd Part 1 Question 1.

Answer: ID, year, month, day

**Question 2: What is the outcome variable? (2 points)**

Instructions: Indicate which columns represent the outcome variable and describe its unit.

Answer: The outcome variable is NO2 emissions and its unit is in 10^16^ molecules per cm\^2

**Question 3: What are the treatment and control variables?** **(4 points)**

Instructions: For this assignment, you will not distinguish between the treatment and control variables. Instead, please list all treatment and control variables. For each variable, indicate whether it is a numerical variable or a categorical variable.

Answer: Our treatment variable was the opening of the lithium ion battery recycling plants. This is a categorical variable as the variable determined whether the lithium ion battery recycling plant was open or not. We did not have any control variables.

### **Part 2. Running a Basic Regression**

**Question 4:** **Given the dataset that you have, in your opinion, what numerical variable is the best predictor of the outcome variable? (1 point)**

Instructions: Choose a numerical variable that would best predict the outcome variable. As we are trying to predict the outcome, this variable does not have to be the treatment variable.

Answer: A numerical variable that could be used to predict the outcome variable is the amount of time that a lithium ion battery recycling plant has been open.

**Question 5: What does the best-fitting line look like between the numerical variable and the outcome variable? (2 points)**

Instructions: Make a scatterplot that shows the relationship between the numerical variable and the outcome variable. In addition, add geom_smooth(method="lm", se=FALSE) to show the best-fitting line. You can also review this concept in this [DataCamp video.](https://campus.datacamp.com/courses/modeling-with-data-in-the-tidyverse/modeling-with-basic-regression?ex=1)

```{r}
# to plot it according to our numerical variable, we need to add a column which contains the number of months that a lithium ion recycling plant has been open

df$opening_month <- ifelse(df$ID == 2, 5, 10)
df$months_open <- ifelse(df$Year < 2022, 0, 0)
df$months_open <- ifelse(df$Year == 2022 & df$opening_month < df$Month, df$Month - df$opening_month, df$months_open)
df$months_open <- ifelse(df$Year == 2023 & df$ID == 2, df$Month + 7, df$months_open)
df$months_open <- ifelse(df$Year == 2023 & df$ID == 3, df$Month + 2, df$months_open)

ggplot(df, aes(x = months_open, y = NO2)) + geom_point() + labs(x = "Months Open", y = "NO2 emission") + geom_smooth(method = "lm", se = FALSE)
```

**Question 6: What is the slope and intercept of the best-fitting line? (2 points)**

Instructions: Fit a regression model with the lm(y\~x, data) function to predict the outcome variable using the numerical variable that you have chosen. You can also review this concept in this [DataCamp video.](https://campus.datacamp.com/courses/modeling-with-data-in-the-tidyverse/modeling-with-basic-regression?ex=1)

```{r}
model_1 <- lm(NO2 ~ months_open, df)
model_1
```

**Question 7: Based on your regression results, what are the values and description of each letter in the equation** $Y_{it} = \beta_0 + \beta_1 X_{it} + \epsilon_{it}$ **(5 points)**

Instructions: For an example of this, you can review asn-6-4-key.qmd Part 1.

$Y_{it}$ represent the outcome variable NO2 emissions for each latitude/longitude (geographical unit) $i$, and month (time unit) $t$.

Based on the regression from Question 6, $\beta_0$ is equal to 2.030e+15.

Based on the regression from Question 6, $\beta_1$ is equal to -8.455e+12.

### **Part 3. Running Multiple Regressions**

**Question 8: Run a multiple regression model that uses all possible numerical variables to predict the outcome variable. What does the regression table look like? (1 point)**

Instructions: You can review how to do this in this [DataCamp](https://campus.datacamp.com/courses/modeling-with-data-in-the-tidyverse/modeling-with-multiple-regression?ex=4) video. Please use the get_regression_table( ) function to print the output.

```{r}
get_regression_table(model_1)
```

**Question 9: What is the sum of squared residuals of the model that you ran in Question 8? (1 point)**

Instructions: You can review how to do this in this [DataCamp](https://campus.datacamp.com/courses/modeling-with-data-in-the-tidyverse/modeling-with-multiple-regression?ex=4) video.

```{r}
get_regression_points(model_1) %>%
  mutate(sq_residuals = residual^2) %>%
  summarize(sum_sq_residuals = sum(sq_residuals))
```

**Question 10: Run a multiple regression model that uses all possible numerical, binary, and categorical variables to predict the outcome variable. What does the regression table look like? (2 points)**

Instructions: A binary variable takes the form of 0 or 1. A categorical variable is a character with only a few unique values.

The efficient way to include categorical variables in a regression is to use the felm( ) function from the lfe package instead of the lm( ) function. The function has the format:

ModelName\<- felm(OutcomeVariable \~ NumericalVariables + BinaryVariables \| Categorical Variables, DataFrame)

The summary(ModelName) function is then used to print out the regression model. An example of this can be found in asn-6-4-key.qmd Part 3 Question 3.

```{r}
#| message: false
install.packages("lfe")
library("lfe")
```

Write your model below and run it.

```{r}
model_all_vars <- felm(NO2 ~ months_open + open, df)
```

**Question 11: What is the sum of squared residuals from the model that you ran in Question 10? (2 points)**

Instructions: Because the function get_regression_points( ) does not work with the function felm( ), you have to replace get_regression_points(ModelName) with ModelName\$residuals. The rest of the code is the same as this [DataCamp](https://campus.datacamp.com/courses/modeling-with-data-in-the-tidyverse/modeling-with-multiple-regression?ex=4) video.

```{r}
sum(model_all_vars$residuals^2)
```

**Question 12: What equation describes the regression in Question 10? What are the values of each coefficient? (2 points)**

Instructions: You can modify the equation shown below. Afterwards, indicate the value of each $\beta$ . To see an example of how categorical variables are written in an equation, see asn-6-4-key.qmd Part 1 Question 4, 5, and 6.

Answer: $Y_{it} = \beta_0 + \beta_1 X_{it} + \epsilon_{it}$

Typically, you would add all of the categorical variables at the end of the equation, but since we don't have any categorical variables, our equation stays the same.

**Question 13: Create more binary or categorical variables by multiplying binary variables or combining categorical variables together as you see fit to better predict the outcome variable. Explain what real-world factor each new variable represents. (2 points)**

Instructions: You created new variables by multiplying binary variables and combining categorical variables in asn-6-4-key.qmd Part 2. You explained what each variable represents in asn-6-4-key.qmd Part 1 Question 4, 5, and 6.

```{r}

```

Answer: Since the only variable that was added was the binary variable open, we do not need to combine it with anything. It represents whether or not the factory was open.

**Question 14: Run a multiple regression model that uses all possible numerical, binary, and categorical variables to predict the outcome variable. What does the regression table look like? (2 points)**

```{r}
model_all_vars <- felm(NO2 ~ months_open + open, df)
```

**Question 15: What is the sum of squared residuals from the model in Question 13? (2 points)**

```{r}
sum(model_all_vars$residuals^2)
```

**Question 16: Based on the sum of squared residuals, which model in this assignment best predicts the outcome? (1 point)**

Answer: The model with all variables, including the binary variable open, seems to slightly better predict the outcome.

### **Part 4. Thinking about causal inference**

Note: Every team except Team Electric Grid and The Whistle Blowers has to complete this part of the assignment.

**Question 17: In your opinion, what are some real-world factors that impact both the treatment and control variables that we have not taken into account? (2 points)**

Answer: Some real world factors is that other things within a certain area can also cause NO2 emissions to change. Since the opening of an EV recycling plant is not the only thing that happens within a certain area, we cannot be certain that there are not other factors that would also impact the NO2 emissions of a certain area.

You have reached the end of this assignment. Commit and push your updates back into the GitHub repository. You can find the step-by-step tutorial [here.](https://drive.google.com/drive/u/0/folders/1eSMfNoV_ilp4OnID2Ql3YT2qXkhCS7Vm)
